---
title: "NC bike crashes"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
library(tidyverse)
ncbikecrash <- read_csv("data/ncbikecrash.csv")
```

## Exercises

#### Exercise 1.

Fill in the blanks for filtering for crashes **not** in Durham County where crash 
year is after 2014 and `bike_position` is not `NA`.

**Note:** You will need to set `eval=TRUE` when you have an answer you want to try out.

```{r filter, eval=FALSE}
ncbikecrash %>%
  filter(
    county ____ "Durham", 
    crash_year ____ 2014,
    ____
    )
```

#### Exercise 2.

How many bike crashes occurred in residential development areas where the 
driver was between 0 and 19 years old?

```{r residential-young-driver}

```

#### Exercise 3.

Create a frequency table of the estimated speed of the car (`driver_est_speed`) 
involved in the crash. What is the most common estimated speed range in the 
dataset?

**Note:** Don't forget to label your R chunk as well (where it says `label-me`). 
Your label should be short, informative, and shouldn't include spaces. It also 
shouldn't repeat a previuous label, otherwise R Markdown will give you an 
error about repeated R chunk labels.

```{r label-me}

```


## Data dictionary

Below is the full data dictionary. Note that it is long (there are lots of variables in the data), but we will be using a limited sed of the variables for our analysis.

- `object_id`: Crash ID
- `city`: City of crash
- `county`: County of crash
- `region`: Region of crash
- `development`: Development area of crash
- `locality`: Locality of crash
- `on_road`: Road where crash happened
- `rural_urban`: Whether crash happened on rural or urban road
- `speed_limit`: Speed limit where crash happened
- `traffic_control`: Type of traffic control where crash happened
- `weather`: Weather at the time of crash
- `workzone`: Whether crash happened in a work zone
- `bike_age`: Age of biker
- `bike_age_group`: Age group of biker
- `bike_alcohol`: Whether biker had alcohol
- `bike_alcohol_drugs`: Whether biker had alcohol or drugs
- `bike_direction`: Direction of bike at the time of crash
- `bike_injury`: Injury of biker
- `bike_position`: Position of bike at the time of crash
- `bike_race`: Race of biker
- `bike_sex`: Sex of biker
- `driver_age`: Age of driver
- `driver_age_group`: Age group of driver
- `driver_alcohol`: Whether driver had alcohol
- `driver_alcohol_drugs`: Whether driver had alcohol or drugs
- `driver_est_speed`: Estimated speed of driver
- `driver_injury`: Injury of driver
- `driver_race`: Race of driver
- `driver_sex`: Sex of driver
- `driver_vehicle_type`: Type of vehicle involved in crash
- `crash_alcohol`: Whether alcohol was involved in crash
- `crash_date`: Date of crash
- `crash_day`: Day of crash
- `crash_group`: Type of crash
- `crash_hour`: Hour of crash
- `crash_location`: Location of crash
- `crash_month`: Month of crash
- `crash_severity`: Severity of crash
- `crash_time`: Time of crash
- `crash_type`: Type of crash
- `crash_year`: Year of crash
- `ambulance_req`: Whether ambulance was required
- `hit_run`: Whether accident was a hit and run
- `light_condition`: Light condition at the time of crash
- `road_character`: Road characteristics
- `road_class`: Road class
- `road_condition`: Road condition
- `road_configuration`: Road configuration
- `road_defects`: Road defects
- `road_feature`: Road feature
- `road_surface`: Road surface
- `num_lanes`: Number of lanes
- `geo_point`: Latitude and longitude of crash
