---
title: "Fisheries"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
library(tidyverse)
fisheries <- read_csv("data/fisheries.csv")
continents <- read_csv("data/continents.csv")
```

The code below brings you to the point in the slides where we left off...

```{r}
fisheries <- fisheries %>%
  filter(total > 100000) %>%
  left_join(continents) %>%
  mutate(
    continent = case_when(
      country == "Democratic Republic of the Congo" ~ "Africa",
      country == "Hong Kong"                        ~ "Asia",
      country == "Myanmar"                          ~ "Asia",
      TRUE                                          ~ continent
      ),
    aquaculture_perc = aquaculture / total
    )
```

1. Calculate the mean aquaculture (we'll call it `mean_ac` for short) percentage 
for counties in the fisheries data using the `summarise()` function in dplyr. 
Note that the function for calculating the mean is `mean()` in R.

```{r fisheries-mean}
fisheries %>%                  # start with the fisheries data frame
  ___(mean_ac = ___)           # calculate mean acquculture
```

2. Now expand your calculations to also calculate the minimum and maximum 
aquacultute percentage for countries in the fisheries data. Note that the 
functions for calculating minimum and maximum in R are `min()` and `max()`
respectively.

```{r fisheries-summary}
fisheries %>%                  # start with the fisheries data frame
  ___(
    mean_ac = ___,             # calculate mean acquculture
    min_ac  = ____,            # calculate min acquculture
    max_ac  = ____             # calculate max acquculture
    )          
```

3. Create a new data frame called `fisheries_summary_continent` that calculates 
minimum, mean, and maximum aquacultute percentage for each continent in the 
fisheries data. 

```{r fisheries-summary-continent}
fisheries_summary_continent <- fisheries %>%
  ___ %>%                      # ensure calculations are done per continent
  ___(
    mean_ac = ___,             # calculate mean acquculture
    min_ac  = ____,            # calculate min acquculture
    max_ac  = ____             # calculate max acquculture
    )                          
```

4. Take the `fisheries_summary_continent` data frame and order the results in descending 
order of mean aquaculture percentage.

```{r fisheries-summary-continent-sorted}
fisheries_summary_continent %>%      # start with the fisheries_summary_continent data frame
  ___                                # order in descending order of mean
```


