---
title: "Iteration <br> `r emo::ji('dancing_women')`"
output:
  xaringan::moon_reader:
    css: "../slides.css"
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightLines: true
      highlightStyle: solarized-light
      countIncrementalSlides: false
---

```{r child = "../setup.Rmd"}
```

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(readxl)
```


class: center, middle

# Copying and pasting...

---

## January data

.small[
```{r}
sales_01 <- read_excel("data-raw/01-sales.xlsx")
sales_01
```
]

---

## Let's try again

```{r}
sales_01 <- read_excel("data-raw/01-sales.xlsx", skip = 3)
sales_01
```

---

## And again

```{r}
sales_01 <- read_excel("data-raw/01-sales.xlsx", skip = 3,
                    col_names = c("id", "n"))
sales_01
```

---

```{r}
sales_01 <- sales_01 %>%
  mutate(month = 1)
sales_01
```

---

## February data

```{r}
sales_02 <- read_excel("data-raw/02-sales.xlsx", skip = 3,
                    col_names = c("id", "n")) %>%
  mutate(month = 2)
sales_02
```

---

## March data

```{r}
sales_03 <- read_excel("data-raw/03-sales.xlsx", skip = 3,
                    col_names = c("id", "n")) %>%
  mutate(month = 3)
sales_03
```

---

class: middle

you get the point...

---

class: middle

.question[
What are some ways you can thin of that would allow us to automate reading these files in all at once so we don't have to repeat ourselves? It's ok if you don't know how to implement it, we're just looking for ideas!
]

---

## Solve the problem with iteration

1. Get a list of all files
2. Map the same function for reading in a single file over this list

---

## Get a list of all files

```{r}
fs::dir_ls("data-raw")
```

---

## Read all files at once

```{r}
sales <- purrr::map_dfr(
  .x = fs::dir_ls("data-raw"), 
  .f = read_excel, 
  skip = 3, col_names = c("id", "n")
  )
glimpse(sales)
```

---

## And keep track of source file

```{r}
sales <- purrr::map_dfr(
  .x = fs::dir_ls("data-raw"), 
  .f = read_excel, 
  skip = 3, col_names = c("id", "n"),
  .id = "source"
  )
glimpse(sales)
```

  

---

### 07 - Iteration / `01-sales-monthly.Rmd` - **Exercise 1**

.instructions[
Read and talk through the code below to get a sense of what is happening 
at each step of the pipeline. Finally, come up with a few other aspects of the 
data frame you would like to clean up to prepare it for analysis. **Stretch goal:** Implement them!  

**Note:** Some of it should feel familiar, e.g. how `is_brand_name` is defined, 
`fill()`, etc.
]

.small[
```{r eval=FALSE}
sales <- sales %>%
  mutate(
    is_brand_name = str_detect(id, "Brand"),
    brand = if_else(is_brand_name, id, NA_character_)
  ) %>%
  fill(brand) %>%
  filter(!is_brand_name) %>%
  rename(month = source) %>%
  select(month, brand, id, n)
```
]

```{r echo=FALSE}
countdown(minutes = 10, seconds = 0)
```

.footnote[
[rstd.io/bootcamper-cloud](https://rstd.io/bootcamper-cloud)
]

---

```{r}
sales <- sales %>%
  mutate(
    is_brand_name = str_detect(id, "Brand"),
    brand = if_else(is_brand_name, id, NA_character_)
  ) %>%
  fill(brand) %>%
  filter(!is_brand_name) %>%
  rename(month = source) %>%
  select(month, brand, id, n) %>%
  # MOAR CLEANING ----
  mutate(
    id = as.numeric(id),
    n = as.numeric(n),
    month = str_remove(month, "-sales.xlsx"),
    month = str_remove(month, "data-raw/"),
    month = as.integer(month)
  )
```

---

```{r}
sales
```

---

### 07 - Iteration / `01-sales-monthly.Rmd` - **Exercise 2**

.instructions[
How many total items were sold each month? How many per brand each month?  
**Hint:** `group_by()` then `summarise()`.
]

.small[
.pull-left[
```{r include=FALSE}
sales %>%
  group_by(month) %>%
  summarise(total_n = sum(n))
```
]
.pull-right[
```{r include=FALSE}
sales %>%
  group_by(month, brand) %>%
  summarise(total_n = sum(n))
```
]
]

---

## What is `map()`?

```{r eval=FALSE}
map(.x, .f = ~ DO SOMETHING WITH .x, ...)
```

> For each element of `.x` do `.f`

- `.x`: a list
- `.f`: a function to apply to each element of `.x`
- `...`: other arguments to pass to function

---

## Student scores

.small[
```{r}
set.seed(1015) # Ensures everyone gets the same random numbers
scores <- list(
  student1 = round(runif(10, 50, 100)),
  student2 = round(runif(10, 50, 100)),
  student3 = round(runif(10, 50, 100)),
  student4 = round(runif(10, 50, 100)),
  student5 = round(runif(10, 50, 100))
)
scores
```
]

---

.question[
What do you think the following does?
]

```{r eval=FALSE}
map(scores, mean)
```

--

```{r echo=FALSE}
map(scores, mean)
```

---

.question[
What would I change to calculate the standard deviation of each students' scores?
```
map(scores, mean)
```
]

--

.midi[
```{r}
map(scores, sd)
```
]

]


---

## `map()` & friends

- Other types of output: `map_something`
- Other ways of specifying `.f` (a formula, a string or integer to extract the named/numbered element for each element, or a function)
- Other iteration functions: `map2` - variants of `map()` that iterate over multiple arguments in parallel

---

## `map_something`

Functions for looping over an object and returning a value (of a specific type):

* `map()` - returns a list
* `map_lgl()` - returns a logical vector
* `map_int()` - returns a integer vector
* `map_dbl()` - returns a double vector
* `map_chr()` - returns a character vector
* `map_df()` / `map_dfr()` - returns a data frame by row binding
* `map_dfc()` - returns a data frame by column binding
* ...

---

.question[
What would I change if I want the output to be a vector, not a list?
```
map(scores, mean)
```
]

--

.midi[
```{r}
map_dbl(scores, mean)
```
]

---

.question[
What if I had `NA`s in the data?
]

.small[
```{r}
scores_with_na <- list(
  student1 = c(round(runif(9, 50, 100)), NA),
  student2 = c(round(runif(9, 50, 100)), NA),
  student3 = c(round(runif(9, 50, 100)), NA),
  student4 = c(round(runif(9, 50, 100)), NA),
  student5 = c(round(runif(9, 50, 100)), NA)
)
scores_with_na
```
]

---

.question[
What if I had `NA`s in the data?
]

```{r}
map_dbl(scores_with_na, mean)
map_dbl(scores_with_na, mean, na.rm = TRUE)
```

---

class: middle

.question[
What if what we wanted to do is not a predefined function?
]

--

Write a function!
