---
title: "Cumulative deaths from COVID-19"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
params: 
  country:
    label: "Country"
    value: US
    input: select
    multiple: yes
    choices: !r unique(coronavirus::coronavirus$Country.Region)
---

## Introduction

Countries around the world are responding to an outbreak of respiratory illness caused by a novel coronavirus, COVID-19. The outbreak first started in Wuhan, China, but cases have been identified in a growing number of other locations internationally, including the United States. In this report we explore how the trajectory of the cumulative deaths in a number of countries.

The data come from the **coronavirus** package, which pulls data from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository. The coronavirus package provides a tidy format dataset of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic. The package is available on GitHub [here](https://github.com/RamiKrispin/coronavirus) and is updated daily.

For our analysis, in addition to the coronavirus package, we will use the **tidyverse** package for data wrangling and visualization and the **ggrepel** package for pretty printing of country labels.

We will also make use of three more packages for formatting output shown throughout the report: 
the **DT** package for interactive display of tabular output, the **knitr** package for formatting tables, and the **glue** package for formatting text output.

```{r load-packages, warning=FALSE, message=FALSE}
library(coronavirus)
library(tidyverse)
library(ggrepel)
library(DT)
library(glue)
```

## Data prep

The data frame called `coronavirus` in the coronavirus package provides a daily summary of the Coronavirus (COVID-19) cases by country. Each row in the data frame represents a country (or, where relevant, state/province). A full list of the countries in the data frame is provided in the [Appendix]. Note that the data provided in this package provides daily number of deaths, confirmed cases, and recovered cases. For this report, we will focus on the deaths. 

We will start by making our selection for the countries we want to explore.

```{r select-countries}
countries <- params$country
```

In the following code chunk we filter the data frame for deaths in the countries we specified above and calculate cumulative number of deaths. We will only visualise data since 10th confirmed death. 

```{r prep-country-data}
country_data <- coronavirus %>%
  # filter for deaths in countries of interest
  filter(
    type == "death",
    Country.Region %in% countries
  ) %>%
  # fix county labels for pretty plotting
  mutate(
    country = case_when(
      Country.Region == "United Kingdom" ~ "UK",
      TRUE ~ Country.Region
    )
  ) %>%
  # calculate cumulative cases
  group_by(country, date) %>%
  summarise(tot_cases = sum(cases)) %>%
  arrange(date) %>%
  mutate(cumulative_cases = cumsum(tot_cases)) %>%
  # only use data where cumulative cases > 10
  filter(cumulative_cases > 9) %>%
  # calculate days elapsed and label for last recorded date for country
  mutate(
    days_elapsed = as.numeric(date - min(date)),
    end_label = ifelse(date == max(date), country, NA)
  )
```

We also need to take a note of the "as of date" for the data so that we can properly label our visualisation.

```{r record-as-of-date}
as_of_date <- format(max(country_data$date), "%A, %B %e, %Y")
```

These data are as of `r as_of_date`.

As the last step in our data prep, let's also take a note of the last data point in our cumulative deaths dataset.

```{r record-last-data-point}
last_data_point <- country_data %>%
  group_by(country) %>%
  filter(date == max(date))

last_data_point
```

This data point will be used to add emphasis to the line endings in our visualisation.

## Visualisation

The following visualisation shows the number of cumulative cases vs. days elapsed since the 10th confirmed death in each country. The time span plotted for each country varies since some countries started seeing (and reporting) deaths from COVID-19 much later than others.

```{r visualise, warning=FALSE}
ggplot(data = country_data, 
       mapping = aes(x = days_elapsed, 
                     y = cumulative_cases, 
                     color = country, 
                     label = end_label)) +
  geom_line(size = 0.7, alpha = 0.8) +
  # use pretty colors
  scale_color_viridis_d() +
  # turn off legend
  guides(color = FALSE) +
  # add country labels, nudged above the lines
  geom_label_repel(nudge_y = 1, direction = "y", hjust = 1) + 
  # add points to line endings
  geom_point(data = last_data_point, 
             mapping = aes(x = days_elapsed, 
                           y = cumulative_cases)) +
  # use minimal theme
  theme_minimal() +
  # customize labels
  labs(
    x = "Days since 10th confirmed death",
    y = "Cumulative number of deaths",
    title = "Cumulative deaths from COVID-19, selected countries",
    subtitle = glue("Data as of", as_of_date, .sep = " "),
    caption = "Source: github.com/RamiKrispin/coronavirus"
  )
```

## Appendix

A list of countries in the `coronavirus` data frame is provided below.

```{r list-countries, echo=FALSE}
coronavirus %>%
  select(Country.Region) %>%
  arrange(Country.Region) %>%
  distinct() %>%
  datatable()
```
