---
title: "Cumulative deaths from COVID-19"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

In this exercise we will recreate the coronavirus visualisation we started off with, step by step.

Let's start by loading the packages we will use. Note that we're using `warning=FALSE` and `message=FALSE` to suppress warnings and messages that get printed out when loading packages. This is useful for keeping your report clean, but you might want to set them to `TRUE` temporarily to see what is printed out.

```{r load-packages, warning=FALSE, message=FALSE}
library(coronavirus)
library(tidyverse)
library(ggrepel)
library(DT)
library(glue)
```

## Data prep

The data frame called `coronavirus` in the coronavirus package provides a daily summary of the Coronavirus (COVID-19) cases by country. Each row in the data frame represents a country (or, where relevant, state/province). A full list of the countries in the data frame is provided in the [Appendix]. Note that the data provided in this package provides daily number of deaths, confirmed cases, and recovered cases. For this report, we will focus on the deaths. 

We will start by making our selection for the countries we want to explore.

```{r select-countries}
countries <- c(
  "US",
  "Germany",
  "____" # add another country of your choosing here
)
```

glue::glue("{wday(x, label = TRUE)}, {month(x, label = TRUE)} {day(x)}, {year(x)} ")


The following are step by step instructions for getting the data formatted for the eventual visualisation we will make. Fill in the blanks.

1. Filter the data for "deaths". Note that type can take on the following values: `confirmed`, `death`, `recovered`.

```{r}
coronavirus %>%
  # filter for deaths
  filter(type == "___")
```

2. Calculate cumulative cases.


In the following code chunk we filter the data frame for deaths in the countries we specified above and calculate cumulative number of deaths. We will only visualise data since 10th confirmed death. 

```{r prep-country-data}
country_data <- coronavirus %>%
  # filter for deaths in countries of interest
  filter(
    type == "death",
    Country.Region %in% countries
  ) %>%
  # calculate cumulative cases
  group_by(country, date) %>%
  summarise(tot_cases = sum(cases)) %>%
  arrange(date) %>%
  mutate(cumulative_cases = cumsum(tot_cases)) %>%
  # only use data where cumulative cases > 9
  filter(cumulative_cases > 9) %>%
  # calculate days elapsed and label for last recorded date for country
  mutate(
    days_elapsed = as.numeric(date - min(date)),
    end_label = ifelse(date == max(date), country, NA)
  )
```

We also need to take a note of the "as of date" for the data so that we can properly label our visualisation.

```{r record-as-of-date}
as_of_date <- format(max(country_data$date), "%A, %B %e, %Y")
```

These data are as of `r as_of_date`.

As the last step in our data prep, let's also take a note of the last data point in our cumulative deaths dataset.

```{r record-last-data-point}
last_data_point <- country_data %>%
  group_by(country) %>%
  filter(date == max(date))

last_data_point
```

This data point will be used to add emphasis to the line endings in our visualisation.

## Visualisation

The following visualisation shows the number of cumulative cases vs. days elapsed since the 10th confirmed death in each country. The time span plotted for each country varies since some countries started seeing (and reporting) deaths from COVID-19 much later than others.

```{r visualise, warning=FALSE}
ggplot(data = country_data, 
       mapping = aes(x = days_elapsed, 
                     y = cumulative_cases, 
                     color = country, 
                     label = end_label)) +
  geom_line(size = 0.7, alpha = 0.8) +
  # use pretty colors
  scale_color_viridis_d() +
  # turn off legend
  guides(color = FALSE) +
  # add country labels, nudged above the lines
  geom_label_repel(nudge_y = 1, direction = "y", hjust = 1) + 
  # add points to line endings
  geom_point(data = last_data_point, 
             mapping = aes(x = days_elapsed, 
                           y = cumulative_cases)) +
  # use minimal theme
  theme_minimal() +
  # customize labels
  labs(
    x = "Days since 10th confirmed death",
    y = "Cumulative number of deaths",
    title = "Cumulative deaths from COVID-19, selected countries",
    subtitle = glue("Data as of", as_of_date, .sep = " "),
    caption = "Source: github.com/RamiKrispin/coronavirus"
  )
```

## Appendix

A list of countries in the `coronavirus` data frame is provided below.

```{r list-countries, echo=FALSE}
coronavirus %>%
  select(Country.Region) %>%
  arrange(Country.Region) %>%
  distinct() %>%
  datatable()
```
